Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Fix 0.7 standard deviation

Surprisingly, although we ran a large number of experiments to formulate the relevance-based quantization scheme into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in \emph{late} temporal integration, namely majority voting. Among such methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm0.7$. \ja{Why don't we display these results? Also how is the variance so much smaller here?} \ml{I agree, we should put the results} This might be due to the fact that the discriminability gained by the relevance-based quantization approach is already achieved by the classifiers during training and the fact the relevance-based quantization approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}). \ja{This sentence is very confusing.}

>>>>

Surprisingly, although we ran a large number of experiments to formulate the relevance-based quantization scheme into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in \emph{late} temporal integration, namely majority voting. Among such methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm 7$. \ja{Why don't we display these results?} \ml{I agree, we should put the results} This might be due to the fact that the discriminability gained by the relevance-based quantization approach is already achieved by the classifiers during training and the fact the relevance-based quantization approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}). \ja{This sentence is very confusing.}
